---
title: "Analysis - Inside_Airbnb :City - Paris, France"
output: word_document
---

# Detailed Analysis

## Prerequisits
******************************************************

```{r}
setwd("C:/Personal/Books/MSc. in Applied Statistics/MAS 5112 - Exploratory Data Analysis/Group Project 1/Inside_Airbnb_City_Paris_France")
library(ggplot2)
library(sf)
library(geojsonR)
library(tidyverse)
library(ggpubr)
library(reshape2)
```

\newpage
### Load special data (shape data) France-Paris
******************************************************

```{r}
# Load special data (shape data) France-Paris
paris = st_read("neighbourhoods.geojson")

# Load Cleaned Airbnb Data, France-Paris
ab_data <- read_csv("listing_cleaned.csv") 
```
\newpage
## Spread of Accommodations and their prices

### Accommodation Spread
******************************************************

```{r}
neighborhoods_loc <- ab_data %>% group_by(neighbourhood) %>% summarise(longitude = mean(longitude), latitude = mean(latitude)) 
neighborhoods_loc$index <- c(1:20)

hot_spot1 <- neighborhoods_loc %>% filter((index == 3))
hot_spot2 <- neighborhoods_loc %>% filter((index == 5))
hot_spot3 <- neighborhoods_loc %>% filter((index == 19))
hot_spot4 <- neighborhoods_loc %>% filter((index == 8))

#glimpse(neighborhoods_loc)

base <- ggplot(paris) +
   geom_sf() 

base +
    geom_text(data=neighborhoods_loc, 
              aes(x=longitude, y=latitude, label=index)) + 
    stat_density2d(data=ab_data, 
                   aes(x=longitude, y=latitude, fill = ..density..), 
                   geom='tile', contour = F, alpha = .6) +
    viridis::scale_fill_viridis(option='inferno') + 
    geom_segment(data = hot_spot1, 
                 aes(x=longitude, y=latitude, xend=2.275, yend=48.9)) +
    geom_segment(data = hot_spot2, 
                 aes(x=longitude, y=latitude, xend=2.41, yend=48.9)) +
    geom_segment(data = hot_spot3, 
                 aes(x=longitude, y=latitude, xend=2.425, yend=48.87)) +
    geom_segment(data = hot_spot4, 
                 aes(x=longitude, y=latitude, xend=2.43, yend=48.88)) +
    geom_label(data = hot_spot1, aes(label = neighbourhood, x=2.275, y=48.9)) + 
    geom_label(data = hot_spot2, aes(label = neighbourhood, x=2.41, y=48.9)) +
    geom_label(data = hot_spot3, aes(label = neighbourhood, x=2.425, y=48.87)) +
    geom_label(data = hot_spot4, aes(label = neighbourhood, x=2.43, y=48.88)) +
    labs(title = "Paris - Accomodation Densities by Neighbourhoods",
       x = NULL,
       y = NULL) 

```
There is clear evidence that most of the accommodations are located in Neighborhoods: "Bourse", "Temple", "L'Entrepot", and "Buttes-Montmartre" (Hot spots).

### Accommodation Prices
******************************************************

```{r}
ggplot(ab_data, aes(x = reorder(room_type, -price), y = price)) + 
  geom_bar(stat = "summary", fun = "mean") +
  labs(title = "Average Price (€) / Day",
       x = NULL,
       y = NULL)+
  theme_minimal() +
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.ontop = TRUE
  )
```
Overall hotel room prices are high comparing to the other accommodation types.

```{r}
ggplot(ab_data) + 
  geom_boxplot(aes(x = price, y = room_type, fill = room_type))+
  scale_x_continuous(limits = c(0, 5000)) + 
  labs(title = "Room Types: Price Comparison",
       x = "Price (€) / Day",
       y = NULL) +
  theme_minimal() +
  theme(legend.position="none")
  
```


In generally "Hotel Room" is the most expensive accommodation option and "Shared Room" is the cost effective option.
But price variation of "Entire Home/Apartment" options is really high. Contains really high end prices.

\newpage
## Quality of service and Price.

### Accomadation: Hotel Rooms
******************************************************

```{r}
hotel_room <- ab_data %>% filter(room_type == 'Hotel room')

# Check reviews
ggplot(hotel_room, aes(y = reorder(neighbourhood, number_of_reviews), 
                        x = number_of_reviews, #)) + 
                        fill=factor(ifelse((neighbourhood=="Observatoire")|
                                             (neighbourhood=="Buttes-Montmartre")|
                                             (neighbourhood=="Bourse"),
                                           "High Reviews",
                                           "Not high")))) +
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#F7C815","grey50")) +
  labs(title = "Room Type: Hotel Rooms - Reviews",
       x = "Average Reviews",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )

# Check prices
ggplot(hotel_room, aes(y = reorder(neighbourhood, price), 
                        x = price, #)) + 
                        fill=factor(ifelse((neighbourhood=="Observatoire")|
                                             (neighbourhood=="Buttes-Montmartre")|
                                             (neighbourhood=="Bourse"),
                                           "High Reviews",
                                           "Not high")))) +
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#F7C815","grey50")) +
  labs(title = "Room Type: Hotel Rooms - Prices",
       x = "Average Price (€) / Day",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )
```
"Observatoire", "Buttes-Montmartre", and "Bourse" are the most highly review neighborhoods for hotel rooms.
"Bourse" is more likely to have good quality high end hotel rooms.
"Observatoire", "Buttes-Montmartre" neighborhoods are ideal for low budget hotel rooms with good quality service.


### Accomodation: Entire home/Appartments
******************************************************

```{r}
entire_home <- ab_data %>% filter(room_type == 'Entire home/apt')

# Check reviews
ggplot(entire_home, aes(y = reorder(neighbourhood, number_of_reviews), 
                        x = number_of_reviews, #)) + 
                        fill=factor(ifelse((neighbourhood=="Louvre")|
                                             (neighbourhood=="Bourse")|
                                             (neighbourhood=="Temple")|
                                             (neighbourhood=="Hotel de Ville"),
                                           "High Reviews",
                                           "Not high")))) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#00A300","grey50")) +
  scale_color_manual(values = c("Louvre" = "Green",
                               "Bourse" = "Green",
                               "Temple" = "Green",
                               "Hotel de Ville" = "Green")) +
  labs(title = "Room Type: Entire home/apt - Reviews",
       x = "Average Reviews",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )

# Check prices
ggplot(entire_home, aes(y = reorder(neighbourhood, price), 
                        x = price, #)) + 
                        fill=factor(ifelse((neighbourhood=="Louvre")|
                                             (neighbourhood=="Bourse")|
                                             (neighbourhood=="Temple")|
                                             (neighbourhood=="Hotel de Ville"),
                                           "High Reviews",
                                           "Not high")))) +
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#00A300","grey50")) +
  labs(title = "Room Type: Entire home/apt - Prices",
       x = "Average Price (€) / Day",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )


```
"Louvre", "Bourse", "Temple", and "Hotel de Ville" are the most highly review neighborhoods for entire homes or apartments.
"Louvre" and "Bourse" are more likely to have good quality high end homes or apartments.
"Temple" and "Hotel de Ville" are more likely to have good quality moderate priced homes or apartments.

### Accomadation: Private Rooms
******************************************************

```{r}
private_room <- ab_data %>% filter(room_type == 'Private room')

# Check reviews
ggplot(private_room, aes(y = reorder(neighbourhood, number_of_reviews), 
                        x = number_of_reviews, #)) + 
                        fill=factor(ifelse((neighbourhood=="Louvre")|
                                             (neighbourhood=="Bourse")|
                                             (neighbourhood=="Hotel de Ville"),
                                           "High Reviews",
                                           "Not high")))) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#AA1803","grey50")) +
  scale_color_manual(values = c("Louvre" = "Green",
                               "Bourse" = "Green",
                               "Temple" = "Green",
                               "Hotel de Ville" = "Green")) +
  labs(title = "Room Type: Private Rooms - Reviews",
       x = "Average Reviews",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )

# Check prices
ggplot(private_room, aes(y = reorder(neighbourhood, price), 
                        x = price, #)) + 
                        fill=factor(ifelse((neighbourhood=="Louvre")|
                                             (neighbourhood=="Bourse")|
                                             (neighbourhood=="Hotel de Ville"),
                                           "High Reviews",
                                           "Not high")))) +
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#AA1803","grey50")) +
  labs(title = "Room Type: Private Rooms - Prices",
       x = "Average Price (€) / Day",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )
```
"Louvre", "Hotel de Ville", and "Bourse" are the most highly review neighborhoods for private rooms.
"Louvre" and "Bourse" are more likely to have good quality high end private rooms.
"Hotel de Ville" is more likely to have good quality moderate priced private rooms.

### Accomadation: Shared Rooms
******************************************************

```{r}
shared_room <- ab_data %>% filter(room_type == 'Shared room')

# Check reviews
ggplot(shared_room, aes(y = reorder(neighbourhood, number_of_reviews), 
                        x = number_of_reviews, #)) + 
                        fill=factor(ifelse((neighbourhood=="Reuilly")|
                                             (neighbourhood=="Opera")|
                                             (neighbourhood=="Bourse"),
                                           "High Reviews","Not high")))) + 
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#2F70AF","grey50")) +
  scale_color_manual(values = c("Louvre" = "Green",
                               "Bourse" = "Green",
                               "Temple" = "Green",
                               "Hotel de Ville" = "Green")) +
  labs(title = "Room Type: Shared Rooms - Reviews",
       x = "Average Reviews",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )

# Check prices
ggplot(shared_room, aes(y = reorder(neighbourhood, price), 
                        x = price, #)) + 
                        fill=factor(ifelse((neighbourhood=="Reuilly")|
                                             (neighbourhood=="Opera")|
                                             (neighbourhood=="Bourse"),
                                           "High Reviews",
                                           "Not high")))) +
  geom_bar(stat = "summary", fun = "mean")+
  scale_fill_manual(name = "Reviews", values=c("#2F70AF","grey50")) +
  labs(title = "Room Type: Shared Rooms - Prices",
       x = "Average Price (€) / Day",
       y = NULL) +
  theme_minimal() + 
  theme(
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )


```
"Reuilly", "Opera", and "Bourse" are the most highly review neighborhoods for shared rooms.
"Bourse" is more likely to have good quality moderate priced shared rooms.
"Reuilly" and "Opera" are ideal for low budget shared rooms with good quality service.

\newpage
## Safety 

### Overall Accommodation licensing
******************************************************

```{r}
licensed_info <- ab_data %>% group_by(room_type) %>% 
  count(license_cat, name = "n") %>% 
  pivot_wider(names_from = license_cat, values_from = n, values_fill = 0) %>% 
  ungroup()

licensed_info$total <- licensed_info$Licensed + 
  licensed_info$`License Not Available`+ 
  licensed_info$`Mobile Lease License`+
  licensed_info$`License Exempt`

licensed_info$Licensed_Percent <- 
  (licensed_info$Licensed)/(licensed_info$total)*100
licensed_info$Non_Licensed_Percent <- 
  (licensed_info$`License Not Available`)/(licensed_info$total)*100
licensed_info$Mobile_Lease_Percent <- 
  (licensed_info$`Mobile Lease License`)/(licensed_info$total)*100
licensed_info$License_Exempt_Percent <- 
  (licensed_info$`License Exempt`)/(licensed_info$total)*100

licensed_info <- data.frame(
  room_type = licensed_info$room_type,
  Licensed = licensed_info$Licensed_Percent,
  Non_Licensed = licensed_info$Non_Licensed_Percent,
  Mobile_Lease = licensed_info$Mobile_Lease_Percent,
  License_Exempt = licensed_info$License_Exempt_Percent)

licensed_info <- melt(licensed_info, id.vars=c("room_type"))


licensed_info$ord.x <- factor(licensed_info$variable, ordered=TRUE, 
                              levels = c("Licensed", "Mobile_Lease",
                                         "License_Exempt", "Non_Licensed"))
licensed_info$ord.y <- factor(licensed_info$room_type, ordered=TRUE, 
                              levels = c("Shared room", "Private room",
                                         "Entire home/apt", "Hotel room"))

ggplot(licensed_info) +
  geom_tile(aes(y = ord.y, x = ord.x, fill= value)) +
  scale_fill_viridis_c(option = "inferno", direction=-1) +
  labs(title = "Licensing Status",
            fill = "Percentage (%)",
            x = NULL,
            y = NULL)+
  theme_minimal()
```
Overall around 60% of "Entire home/apt" are licensed.
Overall majority of the "Shared rooms" are not licensed.

### Neighbourhood Level: Accommodation licensing
******************************************************

```{r}
license_type_pivot2 <- ab_data %>% group_by(neighbourhood) %>% 
  count(license_cat, name = "n") %>% 
  pivot_wider(names_from = license_cat, values_from = n, values_fill = 0) %>% 
  ungroup()

license_type_pivot2$total <- license_type_pivot2$Licensed+ 
  license_type_pivot2$`License Not Available`+ 
  license_type_pivot2$`Mobile Lease License`+
  license_type_pivot2$`License Exempt`

license_type_pivot2$Licensed_Percent <- (
  license_type_pivot2$Licensed)/(license_type_pivot2$total)*100
license_type_pivot2$Non_Licensed_Percent <- (
  license_type_pivot2$`License Not Available`)/(license_type_pivot2$total)*100
license_type_pivot2$Mobile_Lease_Percent <- (
  license_type_pivot2$`Mobile Lease License`)/(license_type_pivot2$total)*100
license_type_pivot2$License_Exempt_Percent <- (
  license_type_pivot2$`License Exempt`)/(license_type_pivot2$total)*100

license_type_pivot2 <- data.frame(
  neighbourhood = license_type_pivot2$neighbourhood,
  Licensed = license_type_pivot2$Licensed_Percent,
  Non_Licensed = license_type_pivot2$Non_Licensed_Percent,
  Mobile_Lease = license_type_pivot2$Mobile_Lease_Percent,
  License_Exempt = license_type_pivot2$License_Exempt_Percent)

license_type_pivot2 <-data.frame(license_type_pivot2, row.names = 1)

license_type_pivot2 <- license_type_pivot2 %>% arrange(-Licensed, -Non_Licensed)

ggballoonplot(license_type_pivot2, fill = "value", size.range = c(1, 8)) +
  scale_fill_viridis_c(option = "C")+
  guides(size = FALSE) + 
  labs(title = "Percentages: License Type",
       fill = 'Percentage (%)',
       x = NULL,
       y = NULL)
```
Majority of the accommodations are licensed in neighborhood "Bourse".
"Temple", "Louvre", "Hotel de Ville" follows respectively.

\newpage
## Demand for the accomadation

### Availability
******************************************************

```{r}
availability <- ab_data %>% group_by(neighbourhood, room_type) %>% 
  summarise(mean_availability = mean(availability_365))

availability_pivot2 <- availability %>% 
  pivot_wider(names_from = room_type, 
              values_from = mean_availability, 
              values_fill = 0) %>% 
  ungroup()

availability_pivot2 <- data.frame(
  neighbourhood = availability_pivot2$neighbourhood,
  Hotel_Room = availability_pivot2$`Hotel room`,
  Shared_Room = availability_pivot2$`Shared room`,
  Private_Room = availability_pivot2$`Private room`,
  Entire_Home = availability_pivot2$`Entire home/apt`)

availability_pivot2 <- availability_pivot2 %>% 
  arrange(-Hotel_Room, -Shared_Room, -Private_Room, -Entire_Home)
                                                       
availability_pivot2 <-data.frame(availability_pivot2, row.names = 1)

ggballoonplot(availability_pivot2, fill = "value", size.range = c(1, 8)) +
  scale_fill_viridis_c(option = "viridis")+
  guides(size = FALSE) + 
  labs(title = "Accommodation Availability 365",
       fill = "Avg. Available Days/365",
       x = NULL,
       y = NULL)
```
Overall "Private Rooms" and "Entire Home/Apartments" are highly demanded and less available.
In any neighborhood it is easy to find available "Hotel Room".
Overall "Buttes-Montmartre", "Buttes-Chaumont", "Opera", and "Bourse" highly highly demanded and less available neighborhoods. 

\newpage
## Rules and Conditions

### Rules: Minimum Nights
******************************************************

```{r}
min_nights <- ab_data %>% group_by(neighbourhood, room_type) %>% 
  summarise(mean_min_nights = mean(minimum_nights))

min_nights_pivot <- min_nights %>% 
  pivot_wider(names_from = room_type, 
              values_from = mean_min_nights, 
              values_fill = 0) %>% 
  ungroup()

min_nights_pivot <- data.frame(
  neighbourhood = min_nights_pivot$neighbourhood,
  Hotel_Room = min_nights_pivot$`Hotel room`,
  Shared_Room = min_nights_pivot$`Shared room`,
  Private_Room = min_nights_pivot$`Private room`,
  Entire_Home = min_nights_pivot$`Entire home/apt`)

min_nights_pivot <- min_nights_pivot %>% 
  arrange(-Hotel_Room, -Shared_Room, -Private_Room, -Entire_Home)
                                                       
min_nights_pivot <-data.frame(min_nights_pivot, row.names = 1)

ggballoonplot(min_nights_pivot, fill = "value", size.range = c(1, 8)) +
  scale_fill_viridis_c(option = "inferno", direction=-1)+
  guides(size = FALSE) + 
  labs(title = "Rule: Minimum Nights per Booking",
       fill = "Avg. Minimum Nights",
       x = NULL,
       y = NULL)
```
Overall "Entire Home/Apartment" type accommodations are come up with more conditions. Expecting a longer booking period.
"Share Rooms" and "Private Rooms" bookings are more flexible and associated with less conditions.
Hotel room bookings in "Buttes-Chaumont", and "Menilmontant" are associated with high conditions.

### Per day prices with minimum nights
******************************************************

```{r}
ggplot(ab_data) + 
  geom_point(aes(x = minimum_nights, y = price, color = room_type)) + 
  scale_x_continuous(limits = c(0, 400)) +
  scale_y_continuous(limits = c(0, 1000)) +
  #geom_abline(slope = 100, intercept = 365, colour = 'red') +
  geom_vline(xintercept = 365, size = 4, alpha = 0.15) + 
  facet_wrap(~ room_type) +
  labs(title = "Per Day Prices by Number of Nights",
       y = "Price (€) / Day",
       x = "Min. Nights",
       name = "Room Type") +
  theme_minimal() +
  theme(legend.position="none")

```
Generally for any accommodation type except "Hotel rooms", price per day reduces when booking period increases. 
Hotel rooms are more likely to have fix per day prices.
But there is an exception when it comes to "Entire home/apt" and "Hotel room" type with booking for ONE YEAR. Seems a popular option.

\newpage
## Summary
******************************************************

- "Hotel rooms" prices are generally high but highly available.
- "Share rooms" are the most cost effective and more flexible option.
- "Entire Home/Apartment" accommodation type is the most safest option and generally associated with more rules.
- You are able to find better prices when booking an accommodation for longer period. 
- "Observatoire", "Buttes-Montmartre", and "Bourse" neighborhoods are ideal for "Hotel Room" bookings.
- "Louvre", "Bourse", "Temple", and "Hotel de Ville" neighborhoods are ideal for "Entire Home/Apartment" bookings.
- "Louvre", "Hotel de Ville", and "Bourse" neighborhoods are ideal for "Private Room" bookings.
- "Reuilly", "Opera", and "Bourse" neighborhoods are ideal for "Shared Room" bookings.
- Overall "Bourse" is the most visitor friendly neighborhood.