---
title: "Check Data Integrity - Inside_Airbnb :City - Paris, France"
output: word_document
---

# Check Data Integrity

## Prerequisits
****************************************

```{r}
library(tidyverse)
#tinytex::install_tinytex()
setwd("C:/Personal/Books/MSc. in Applied Statistics/MAS 5112 - Exploratory Data Analysis/Group Project 1/Inside_Airbnb_City_Paris_France")
```

## Load data with approprivate data types
****************************************

```{r}
listings <- read_csv('listings.csv',                     
                    col_types = cols(
                        id = col_character(),
                        name = col_character(),
                        host_id = col_character(),
                        host_name = col_character(),
                        neighbourhood_group = col_character(),
                        neighbourhood = col_character(),
                        latitude = col_double(),
                        longitude = col_double(),
                        room_type = col_character(),
                        price = col_double(),
                        minimum_nights = col_integer(),
                        number_of_reviews = col_integer(),
                        last_review = col_date(format = ""),
                        reviews_per_month = col_double(),
                        calculated_host_listings_count = col_integer(),
                        availability_365 = col_integer(),
                        number_of_reviews_ltm = col_integer(),
                        license = col_character())
                    )
```


## Check shape of the data
****************************************

```{r pressure, echo=FALSE}
head(listings)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
summary(listings)
```
```{r}
print('Columns:')
print(colnames(listings))

cat("\nDimensions:")
print(dim(listings))
```


\newpage
## Identity problems with Data


### Column_01: 'id'
****************************************

```{r}
# Check number of unique values
listings %>% select(id) %>% unique() %>% count()
```
```{r}
# Check number of null values
listings %>% filter(is.na(id)) %>% count()
```
Column 'id':  
  No null values.  
  56739 unique values which matches with the total number of entries.  
  No issues.
  

### Column_02: 'name'
****************************************

```{r}
# Check number of unique values
listings %>% select(name) %>% unique() %>% count()
```
```{r}
# Check number of null values
listings %>% filter(is.na(name)) %>% count()
```
Column 'name':  
  43 null values exists.  
  Out of 56739 rows there are 54742 unique values which means there are duplicate names.  
  Including special characters.
  Less important for statistical analysis.
  

### Column_03: 'host_id'
****************************************

```{r}
# Check number of unique values
listings %>% select(host_id) %>% unique() %>% count()
```
```{r}
# Check number of null values
listings %>% filter(is.na(host_id)) %>% count()
```
Column 'host_id':  
  No null values.  
  Out of 56739 rows there are 43723 unique values which means there are multiple entries for same host id.  
  Nothing to fix in data, be aware that there are multiple entries.
  

### Column_04: 'host_name'
****************************************

```{r}
# Check number of unique values
listings %>% select(host_name) %>% unique() %>% count()
```
```{r}
# Check number of null values
listings %>% filter(is.na(host_name)) %>% count()
```
Column 'host_name':  
  There are 12 null values.  
  Out of 56739 rows there are 9153 unique values which means there are multiple entries.  
  Since this field represent persons name it is less important, can be deleted.
  
  
### Column_05: 'neighbourhood_group'
**************************************** 

```{r}
# Check number of null values
listings %>% filter(is.na(neighbourhood_group)) %>% count()
```
Column 'neighbourhood_group':  
  Empty column.  
  Neighborhood group data is not available for the city- Paris.  
  Can be deleted.
  

### Column_06: 'neighbourhood'
**************************************** 

```{r}
# Check number of unique values
listings %>% select(neighbourhood) %>% unique() %>% count()
```
```{r}
# Check number of null values
listings %>% filter(is.na(neighbourhood)) %>% count()
```
Column 'neighbourhood':  
  No null values.  
  20 unique values.  
  Including special characters.
  
  
### Column_07: 'latitude'
**************************************** 

```{r}
# Check number of null values
listings %>% filter(is.na(latitude)) %>% count()
```
Column 'latitude':  
  No null values.  
  No issues.
  

### Column_08: 'longitude'
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(longitude)) %>% count()
```

Column 'longitude':  
  No null values.  
  No issues.
 

### Column_09: 'room_type'
****************************************

```{r}
# Check number of unique values
listings %>% select(room_type) %>% unique() %>% count()
```
```{r}
listings %>% select(room_type) %>% unique()
```
```{r}
# Check number of null values
listings %>% filter(is.na(room_type)) %>% count()
```
Column 'room_type':  
  No null values. 
  There are four categories ['Entire home/apt', 'Private room', 'Shared room', 'Hotel room'].
  No issues.
  
  
### Column_10: 'price'
**************************************** 

```{r}
# Check number of null or zero values
listings %>% filter(price == 0 | is.na(price)) %>% count()
``` 
Column 'price':  
  There are 29 null or zero price entries. 
  Need to fill zero values by 'room_type' taking in to account.
  

### Column_11: 'minimum_nights'
****************************************

```{r}
# Check number of null or zero values
listings %>% filter(minimum_nights == 0 | is.na(minimum_nights)) %>% count()
``` 
Column 'minimum_nights':  
  Non-zero values exists for all entries. 
  No issues.
  

### Column_12: 'number_of_reviews'
****************************************  

```{r}
# Check number of null values
listings %>% filter(is.na(number_of_reviews)) %>% count()
```
```{r}
# Check for no reviews
listings %>% filter(number_of_reviews == 0) %>% count()
```

Column 'number_of_reviews':  
  No null values. 
  There are 11458 entries with no reviews.
  No issues.
  
  
### Column_13: 'last_review'
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(last_review)) %>% count()
```
This figure (11458) is compatible with number of entries with no reviews.
It is important to check whether those entries with non-zero value for 'number_of_reviews' has a 'last_review' (date)
```{r}
# Check 'number_of_reviews' against 'last_review' (date)
listings %>% filter((number_of_reviews != 0) & is.na(last_review)) %>% count()
```
```{r}
listings %>% filter((number_of_reviews == 0) & (!is.na(last_review))) %>% count()
```
Column 'last_review':  
  All non-zero entries for 'number_of_reviews' field have non empty 'last_review' (date).
  No issues with the data.
  It is recommended to rename 'last_review' column as 'last_review_date' which is more meaningful.
  

### Column_14: 'reviews_per_month'
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(reviews_per_month)) %>% count()
```
```{r}
# Check 'number_of_reviews' and 'reviews_per_month'
listings %>% filter(is.na(reviews_per_month)) %>% select(number_of_reviews, reviews_per_month)
```
```{r}
# Check 'number_of_reviews' against 'reviews_per_month'
listings %>% filter((number_of_reviews != 0) & (is.na(reviews_per_month)|(reviews_per_month == 0))) %>% count()
```
Column 'reviews_per_month':  
  All non-zero entries for 'number_of_reviews' field have non empty or non-zero 'reviews_per_month' value.
  Fill null values with zero.
  
  
### Column_15: 'calculated_host_listings_count'
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(calculated_host_listings_count)) %>% count()
```
Column 'calculated_host_listings_count':  
  No issues with the data.
  Need to understand what this figure means.


### Column_16: 'availability_365'  
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(availability_365)) %>% count()
```
```{r}
# Check number of zero values
listings %>% filter(availability_365 == 0) %>% count()
```
```{r}
#listings %>% filter(availability_365 == 0)
```
```{r}
#listings %>% filter(availability_365 == 365)
```
Column 'availability_365':  
  No null values.
  No issues.
  

### Column_17: 'number_of_reviews_ltm'
****************************************

```{r}
# Check number of null values
listings %>% filter(is.na(availability_365)) %>% count()
```
Column 'number_of_reviews_ltm':  
  No null values.
  It is recommended to rename this column as 'number_of_reviews_last_month' which is more meaningful.


### Column_18: 'license'
**************************************** 

```{r}
# Check number of null values
listings %>% filter(is.na(license)) %>% count()
```
Column 'license':  
  All most half of the entries have 'license' value.
  Fill null values.
  
\newpage

## Summary
**************************************** 

Column:			             |Description
------------------------ |-------------------------------------
'id':  			             |No issues.
'name':			             |Remove field.
'host_id':			         |No issues. Be aware that there are multiple entries.
'host_name':		         |Remove field.
'neighbourhood_group':	 |Remove field.
'neighbourhood':		     |Including special characters.
'latitude':			         |No issues.
'longitude':		         |No issues.
'room_type':		         |No issues.
'price':			           |Fill zero values. (Considering room type)
'minimum_nights':		     |No issues.
'number_of_reviews':	   |No issues.
'last_review':		       |Rename 'last_review' column as 'last_review_date'.
'reviews_per_month':	   |Fill null values with zero.
'calculated_host_listings_count': |No issues.
'availability_365':	     |No issue.
'number_of_reviews_ltm': |Rename 'number_of_reviews_ltm' column as 'number_of_reviews_last_month'.
'license':			         |Fill null values.
  

